%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rishi Shah 
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[utf8]{inputenc}
\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[colorlinks = true, linkcolor = MidnightBlue, urlcolor  = MidnightBlue, citecolor = MidnightBlue, anchorcolor = MidnightBlue]{hyperref}
\usepackage{enumitem}
%----------------------------------------------------------------------------------------
%	HEADER SECTION
%----------------------------------------------------------------------------------------

\name{Thiago Holleben} % Your name
\address{\href{mailto:hollebenthiago@dal.ca}{hollebenthiago@dal.ca}~$\cdot$~ \href{https://www.mathstat.dal.ca/~thiagoh/}{website}}

\begin{document}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
{\bf Universidade Federal do Rio de Janeiro, Brazil} \hfill {\em march 2016 - july 2017 (interrupted)} 
\\ Major in Mathematics\\
{\bf Universidade Federal do Rio de Janeiro, Brazil} \hfill {\em july 2017 - 2020} 
\\ Bachelor in Applied Mathematics
\\
\\{\bf Universidade Federal do Rio de Janeiro, Brazil} \hfill {\em august 2019 - december 2021} 
\\ Master's degree in Mathematics
\\ Dissertation title: \href{https://hollebenthiago.github.io/msc/main.pdf}{The log-concavity of chromatic polynomials}.
\\ Advisor: Seyed Hamid Hassanzadeh
\\
\\{\bf Dalhousie University, Canada} \hfill {\em september 2022 - current} 
\\ PhD in Mathematics
\\ Advisor: Sara Faridi

\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL SSKILLS SECTION
%----------------------------------------------------------------------------------------


%--------------------------------------------------------------------------------
%    Projects SECTION
%-----------------------------------------------------------------------------------------------
% \begin{rSection}{Computational Algebra personal projects}
% {\bf Some simulations on statistical properties of Betti tables over a given class of ideals}
% \\
% Macaulay2 and Python script to study some statistical properties of Betti tables over a given class of ideals.
% \\
%  {\scriptsize Technologies used: Macaulay2, Python3, github repository:  \href{https://github.com/hollebenthiago/Quantitative-Betti-Tables}{Quantitative-Betti-Tables}}
% \\
% {\bf Algorithms related to Elliptic Curves, prime factorization and cryptography.}
% \\
% Webpage that includes some statistical properties of rational points of elliptic curves over finite fields related to Serre's bound, a simple cryptography scheme and Lenstra's algorithm on factorization.
% \\
%  {\scriptsize Technologies used: Javascript, link:  \href{https://hollebenthiago.github.io/ecc/}{Webpage}}

% \end{rSection}

%----------------------------------------------------------------------------------------
%	ACADEMIC SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Academic Achievements}
{\bf Professor Michael Edelstein Memorial Graduate Prize (2023)}
\\
Annual prize awarded to a graduate student who shows great promise in the mathematical sciences. 


{\bf Honours undergraduate research project (2018)}
\\
Received an award for best undergraduate research project on the algebraic and combinatorial properties of Edge Ideals.
\\
Advisor: Seyed Hamid Hassanzadeh
\end{rSection}

\begin{rSection}{Papers}

\begin{enumerate}[label={}]
    \item \textit{The weak Lefschetz property and mixed multiplicities of monomial ideals}. (2023) \href{https://arxiv.org/abs/2306.13274}{arxiv:2306.13274} Submitted to Journal of Algebraic Combinatorics.
    \item \textit{The weak Lefschetz property of whiskered graphs}. With Susan M. Cooper, Sara Faridi, Lisa Nicklasson, Adam Van Tuyl.  \href{https://arxiv.org/abs/2306.04393}{arxiv:2306.04393}. Lefschetz Properties: Current and New Directions, Springer INdAM series, to appear. 
\end{enumerate}
\end{rSection}

\begin{rSection}{In progress}

    \begin{enumerate}[label = {}]
        \item \textit{Computing homotopy type and homological invariants of independence complexes of ternary graphs}. With Sara Faridi.  (preprint, to be submitted November 2023).
        \item \textit{Rees algebras and Lefschetz properties of squarefree monomial ideals}.
        \item \textit{Powers of a simplex}. With Trung Chau, Art Duval, Sara Faridi, Susan Morey, Liana \c{S}ega.
        \item \textit{On the weak Lefschetz properties of squarefree Gotzmann ideals}. With Sara Faridi. 
        \item \textit{Pseudomanifolds, generalized whiskerings and the weak Lefschetz property}. With Susan M. Cooper, Sara Faridi, Lisa Nicklasson, Adam Van Tuyl. 
        \item \textit{Edge ideals of weighted oriented forests via polarization}. With Manohar Kumar. 
    \end{enumerate}
\end{rSection}
%----------------------------------------------------------------------------------------
%	POSITION OF RESPONSIBILITY SECTION
%----------------------------------------------------------------------------------------

\newpage

\begin{rSection}{Presentations}
    \begin{enumerate}[label={}]
        \item \textit{Rees algebras and Lefschetz properties of squarefree monomial ideals}. Commutative Algebra section: CMS winter meeting, Montreal. December 2023 (talk)
        \item \textit{Rees algebras and Lefschetz properties of squarefree monomial ideals}. Stockholm Commutative Algebra seminar. October 2023 (online talk)
        \item \textit{Lefschetz properties of squarefree monomial ideals}. 10th Heidelberg Laureate Forum, Heidelberg University, Germany. September 2023 (poster, lightning talk)
        \item \textit{Lefschetz properties of squarefree monomial ideals}. BrianFest, University of Lincoln-Nebraska. August 2023 (poster)
        \item \textit{Homological Invariants of ternary graphs}. 34o Colóquio Brasileiro de Matemática, Instituto de Matemática Pura e Aplicada, Brazil. July 2023 (poster)
        \item \textit{The weak Lefschetz property and mixed multiplicities of monomial ideals}. MSRI/SLMath Summer School: Commutative Algebra and its Interaction with Algebraic Geometry, Notre Dame university. May 2023 (poster)
        \item \textit{Degree of the inverse of a birational monomial map}. MSRI/SLMath Summer School: Commutative Algebra and its Interaction with Algebraic Geometry, Notre Dame university. May 2023 (lightning talk)
        \item \textit{The weak Lefschetz property and mixed multiplicities of monomial ideals}. Workshop on Lefschetz Properties in Algebra, Geometry, Topology and Combinatorics, Fields institute. May 2023 (talk)
        \item \textit{Lefschetz properties and mixed multiplicities via hyperplane arrangements}. International Centre for Theoretical Physics workshop, Italy. May 2023 (poster)
        \item \textit{The weak Lefschetz property and mixed multiplicities of squarefree monomial ideals}. International Centre for Theoretical Physics summer school, Italy. May 2023 (talk)
        \item \textit{Homological invariants of ternary graphs}. Banff International Research Station workshop: Interactions Between Topological Combinatorics and Combinatorial Commutative Algebra. April 2023 (talk)
        \item \textit{Homological invariants of ternary graphs}. Southern Regional Algebra Conference, Tulane university. March 2023 (online talk)
        \item \textit{Homological invariants of ternary graphs}. Combinatorial Algebra meets Algebraic Combinatorics, Waterloo University. January 2023 (poster)
        \item \textit{The log-concavity of chromatic polynomials}. Universidade Federal do Rio de Janeiro, Brazil. July 2022 (talk, in portuguese)
        \item \textit{Exploring examples with Macaulay2}. Universidade Federal do Rio de Janeiro, Brazil. July 2022 (talk, in portuguese)
        \item \textit{Hilbert functions in Combinatorics}. Universidade Federal do Rio de Janeiro, Brazil. July 2022 (talk, in portuguese)
        \item \textit{A combinatorial interpretation of the primary decomposition of edge ideals}. Universidade Federal do Rio de Janeiro undergraduate student seminar, Brazil. 2019 (talk, in portuguese)
        \item \textit{A brief dictionary between Algebra and Combinatorics}. Semana de Integração Acadêmica da Universidade Federal do Rio de Janeiro, Brazil 2018 (talk, in portuguese)
    \end{enumerate}
\end{rSection}

\begin{rSection}{Leadership positions}
{\bf Organizer of Week of Applied Mathematics and Mathematical Engineering (SEM$^2$Ap)}
\\
Organized virtual Week of Applied Mathematics and Mathematical Engineering (SEM$^2$Ap) in 2020
{\scriptsize More info on:  \href{http://semap.rio.br/2020/en/}{Webpage},   \href{https://www.youtube.com/channel/UC14NMQ5cOsSuLrAQGGa2T4Q}{Youtube}, 
\href{https://www.instagram.com/semap.rio/}{Instagram}}
\\
{\bf Teaching assistant at Dalhousie university}
\\
Fall of 2022 and Winter of 2023
\\
{\bf Teaching assistant at Universidade Federal do Rio de Janeiro} 
\\
First semester of 2019
\\
{\bf Teaching assistant at Universidade Federal do Rio de Janeiro} 
\\
First and second semester of 2018
\\
{\bf Organizer of weekly student seminar at Universidade Federal do Rio de Janeiro}
\\
Organized weekly seminars at Universidade Federal do Rio de Janeiro during the second semester of 2019.
\end{rSection}

% \clearpage

%----------------------------------------------------------------------------------------
%	EVENTS ATTENDED
%----------------------------------------------------------------------------------------

\begin{rSection}{Events attended}

    \begin{itemize}[label={}]
        \item 10th Heidelberg Laureate Forum 2023 (Heidelberg University, Germany) September, 2023
        \item BrianFest (University of Nebraska-Lincoln) August, 2023
        \item 34o Colóquio Brasileiro de Matemática (Instituto de Matemática Pura e Aplicada, Brazil) July, 2023
        \item Commutative Algebra and its Interaction with Algebraic Geometry (University of Notre Dame) May, 2023
        \item Workshop on Lefschetz Properties in Algebra, Geometry, Topology and Combinatorics. (Fields Institute) May, 2023
        \item Workshop on Commutative Algebra and Algebraic Geometry in Prime Characteristics. (International Centre for Theoretical Physics, Italy) May, 2023
        \item School on Commutative Algebra and Algebraic Geometry in Prime Characteristics. (International Centre for Theoretical Physics, Italy) May, 2023
        \item Interactions Between Topological Combinatorics and Combinatorial Commutative Algebra (Banff International Research Station) April, 2023
        \item Combinatorial Algebra meets Algebraic Combinatorics 2023. (Waterloo University) January, 2023
        \item Combinatorial Algebra meets Algebraic Combinatorics 2020. (Dalhousie University) January, 2020
        \item 1st Joint Meeting Brazil-France in Mathematics. (Instituto de Matemática Pura e Aplicada, Brazil) 2019
        \item 32o Colóquio Brasileiro de Matemática. (Instituto de Matemática Pura e Aplicada, Brazil) 2019
        \item SIMCARA. (Universidade São Paulo: São Carlos, Brazil) 2019
        \item Syzygies, from Theory to Applications. (Universidade Federal da Paraíba, Brazil) 2019
        \item XXV Escola de Álgebra. (Universidade Estadual de Campinas, Brazil) 2018
    \end{itemize}
% \\ 34o Colóquio Brasileiro de Matemática (IMPA) 2023 (poster)
% \\ Commutative Algebra and its Interaction with Algebraic Geometry (University of Notre Dame) 2023 (poster, lightning talk)
% \\ Workshop on Lefschetz Properties in Algebra, Geometry, Topology and Combinatorics. (Fields Institute) 2023 (talk, problem)
% \\ Workshop on Commutative Algebra and Algebraic Geometry in Prime Characteristics. (ICTP) 2023 (poster)
% \\ School on Commutative Algebra and Algebraic Geometry in Prime Characteristics. (ICTP) 2023 (talk)
% \\ Interactions Between Topological Combinatorics and Combinatorial Commutative Algebra (BIRS) 2023 (talk)
% % \\ Southern Regional Algebra Conference 2023. (online talk)
% \\ Combinatorial Algebra meets Algebraic Combinatorics 2023. (Waterloo University) 2023 (poster)%(\href{http://semap.rio.br}{poster} presented)
% \\ Combinatorial Algebra meets Algebraic Combinatorics 2020. (Dalhousie University) 2020
% \\ 1st Joint Meeting Brazil-France in Mathematics. (IMPA) 2019
% \\ 32o Colóquio Brasileiro de Matemática. (IMPA) 2019
% \\ SIMCARA. (USP São Carlos) 2019
% \\ Syzygies, from Theory to Applications. (UFPB) 2019
% \\ XXV Escola de Álgebra. (UNICAMP) 2018
% \\
\end{rSection}

\begin{rSection}{Skills}

    \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
    Programming:\ & Macaulay2, Sage, Python, Javascript, Julia
    \\
    \end{tabular}
    
    \end{rSection}

% \begin{rSection}{Research line}
% I am interested in the study of Combinatorial Commutative Algebra, Computational Algebra and their applications.

% \end{rSection}


\end{document}
